---
title: "HW_ANOVA"
author: "Ivanova Ekaterina"
date: '2022-11-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(dplyr)
library(tibble)
library(tidyr)
library(pairwiseCI)
library(flextable)
library(multcomp)

```


```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
soccer_general <- read.csv("soccer.csv", sep=";")[, 2:6] %>% 
  mutate(Position = as.factor(Position), 
         Nationality = as.factor(Nationality), 
         Age = as.numeric(Age), 
         Height = as.numeric(Height)
  ) %>% 
  filter(Nationality %in% c("Spanish", "Italian", "German", "English", "Argentinian")) 


set.seed(1) 

soccer_wrk <- soccer_general[sample(1:nrow(soccer_general), 150), ] %>% 
    mutate(Nationality = factor(Nationality))

```


# Task 1

Let's produce a standard ANOVA on the sample, the null hypothesis is rejected. Thus, the position on the field is associated with the average height of a football player, since p-value <0.05.

```{r, echo=FALSE, message=FALSE, warning=FALSE}


aov(Height ~ Position, data = soccer_wrk) %>% summary


```

# Task 2

A post-hoc analysis was carried out by the Hothorn-Bretz-Westfall method. Statistically significant differences were revealed between the height of the following pairs of players: Goalkeeper-Defender, Midfielder-Defender, Goalkeeper-Forward, Midfielder-Goalkeeper.

The results obtained in this task converge with those obtained in the first HW.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

m0 <- lm(Height ~ Position, data = soccer_wrk)
HBW.comp <- m0 %>%  glht(linfct = mcp(Position = "Tukey"))

HBW.comp %>% summary()

HBW.comp %>% confint()

par(mar = c(5, 10, 4, 2)+0.1)
HBW.comp %>% plot(xlab = "Height difference (cm)")
par(mar = c(5, 10, 4, 2)+0.1)

```


# Task 2

Based on variance analysis, it can be concluded that the country of a football player is not associated with the average growth of a football player. Thus, in post-hoc analysis, we should observe confidence intervals that intersect 0.



```{r, echo=FALSE, message=FALSE, warning=FALSE}

aov(Height ~ Nationality, data = soccer_wrk) %>% summary


m1 <- lm(Height ~ Nationality, data = soccer_wrk)


HBW.comp1 <- m1 %>%  glht(linfct = mcp(Nationality = "Tukey"))

HBW.comp1 %>% summary()

HBW.comp1 %>% confint()

par(mar = c(5, 10, 4, 2)+0.1)
HBW.comp1 %>% plot(xlab = "Height difference (cm)")
par(mar = c(5, 10, 4, 2)+0.1)

```





