---
title: "HW_Mult_comp"
author: "Ivanova Ekaterina"
date: '2022-11-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(dplyr)
library(tibble)
library(tidyr)
library(pairwiseCI)
library(flextable)

```


```{r, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
soccer_general <- read.csv("soccer.csv", sep=";")[, 2:6] %>% 
  mutate(Position = as.factor(Position), 
         Nationality = as.factor(Nationality), 
         Age = as.numeric(Age), 
         Height = as.numeric(Height)
  ) %>% 
  filter(Nationality %in% c("Spanish", "Italian", "German", "English", "Argentinian")) 


set.seed(1) 

soccer_wrk <- soccer_general[sample(1:nrow(soccer_general), 150), ] %>% 
    mutate(Nationality = factor(Nationality))

```


# CI with adjustment

We will construct pairwise 95% confidence intervals for the difference of the averages for the sample and the general population, including with the Bonferroni correction.

All constructed confidence intervals with Bonferroni correction cover the real differences between the height among different pairs of players.

```{r, echo=FALSE, message=FALSE, warning=FALSE}


res_CI_wrk <- as.data.frame(pairwiseCI(Height ~ Position, soccer_wrk)$byout) 

res_CI_wrk %>%
  mutate(method = NULL) %>%
  relocate(compnames) %>%
  flextable() %>%
  theme_box() %>%
  set_caption("CI for sample means comparisons") 


res_CI_wrk_adj <- as.data.frame(pairwiseCI(Height ~ Position, soccer_wrk, conf.level = 0.975)$byout) 

res_CI_wrk_adj %>%
  mutate(method = NULL) %>%
  relocate(compnames) %>%
  flextable() %>%
  theme_box() %>%
  set_caption("CI for means comparisons with Bonferroni correction") 


res_CI_gen <- as.data.frame(pairwiseCI(Height ~ Position, soccer_general)$byout) 


res_CI_gen %>%
  mutate(method = NULL) %>%
  relocate(compnames) %>%
  flextable() %>%
  theme_box() %>%
  set_caption("CI for general population means comparisons") 


```

# Pairwise test with adjustment

We will conduct pairwise tests without correction for multiplicity, as well as with the correction of Holm and Benjamin-Hochberg.

Null hypotheses about the equality of averages were rejected for the following pairs (the significance level is 0.05): Forward-Defender, Goalkeeper-Defender, Midfielder-Defender, Goalkeeper-Forward, Midfielder-Goalkeeper. All discoveries are true.


```{r, echo=FALSE, message=FALSE, warning=FALSE}


res_none <- as.tibble(format(round(pairwise.t.test(soccer_wrk$Height, soccer_wrk$Position, p.adjust.method = "none",
                pool.sd =  FALSE, paired = FALSE,
                alternative = "two.sided", conf.level = 0.95)$p.value,4), scientific = FALSE))

res_none %>%
  mutate(Position = c("Forward","Goalkeeper" ,"Midfielder")) %>%
  relocate(Position) %>%
  flextable() %>%
  theme_box() %>%
  set_caption("Results of pairwise comparisons without correction for multiplicity") 


res_holm <- as.tibble(format(round(pairwise.t.test(soccer_wrk$Height, soccer_wrk$Position, p.adjust.method = "holm",
                pool.sd =  FALSE, paired = FALSE,
                alternative = "two.sided", conf.level = 0.95)$p.value,4), scientific = FALSE))

res_holm %>%
  mutate(Position = c("Forward","Goalkeeper" ,"Midfielder")) %>%
  relocate(Position) %>%
  flextable() %>%
  theme_box() %>%
  set_caption("Results of pairwise comparisons considering Holm correction") 


res_BH <- as.tibble(format(round(pairwise.t.test(soccer_wrk$Height, soccer_wrk$Position, p.adjust.method = "BH",
                pool.sd =  FALSE, paired = FALSE,
                alternative = "two.sided", conf.level = 0.95)$p.value,4), scientific = FALSE))

res_BH %>%
  mutate(Position = c("Forward","Goalkeeper" ,"Midfielder")) %>%
  relocate(Position) %>%
  flextable() %>%
  theme_box() %>%
  set_caption("Results of pairwise comparisons considering Benjamini-Hochberg correction") 


```









```